# Figure 3

Same as Figure 2. 

## Relevant criticisms

## Proposed approach

## Data exploration

```{r }
data_tidy_hladr_infant <- DataTidyGelaDURT::data_tidy_hladr_infant %>%
  tibble::as_tibble()

data_mod_hladr_infant <- data_tidy_hladr_infant %>%
  dplyr::filter(grepl("infant", pid)) %>%
  dplyr::left_join(
    data_tidy_clin_infant %>%
      dplyr::select(-bcg), 
    by = "pid"
  ) %>%
  dplyr::rename(hladr = hladr_mfi)
data_mod_hladr_infant_cyt <- data_mod_hladr_infant %>%
  dplyr::filter(pop == "cd4_ifng")
data_mod_hladr_infant <- data_mod_hladr_infant %>%
  dplyr::filter(pop != "cd4_ifng")
```

```{r }
pop_to_lab_hladr <- c(
  "mait" = "HLA-DR+\nCD3+ MAIT cells (MFI)",
  "nkt" = "HLA-DR+\nCD3+ NKT cells (MFI)",
  "cd1b" = "HLA-DR+\nCD3+ CD1b-GMM+ T cells (MFI)",
  "gem" = "HLA-DR+\nCD3+ GEM T cells (MFI)",
  "gd" = "HLA-DR+\nCD3+ gdTCR+ (MFI)",
  "cd4" = "HLA-DR+\nCD4+ T cells (MFI)",
  "cd4_ifng" = "HLA-DR+\nIFNg+CD4+ T cells (MFI)"
)
pop_to_lab_hladr <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (MFI)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (MFI)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM+ T cells (MFI)")))),
  "gem" = bquote(paste(plain(paste("GEM T cells (MFI)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste("TCR+ cells (MFI)")))), 
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (MFI)")))), 
  "cd4_ifng" = bquote(paste(plain(paste("IFN")), gamma, plain(paste("+CD4+ T cells (MFI)"))))
)

pop_to_lab_hladr_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

### Response against BCG status

The `asinh` transformation seems appropriate.

```{r }
trans_asinh <- scales::trans_new(
  name = "asinh", 
  transform = asinh, 
  inverse = sinh
)
trans_sqrt <- scales::trans_new(
  name = "sqrt_custom", 
  transform = sqrt, 
  inverse = function(x) x^2
)
ggplot(data_mod_hladr_infant %>%
         dplyr::bind_rows(
           data_mod_hladr_infant %>%
             dplyr::group_by(bcg) %>%
             dplyr::slice(1) %>%
             dplyr::mutate(pop = "cd8")
         ) %>%
         dplyr::mutate(
           bcg = factor(
             bcg, 
             levels = c("no bcg", "bcg")
           ), 
           pop = factor(pop, 
                        levels = c(
                          "cd4", "cd8", "mait", 
                          "nkt", "cd1b", 
                          "gd"
                        ))
         ), 
       aes(x = bcg, y = hladr, fill = bcg)) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_boxplot(outlier.size = 1, 
               outlier.colour = "gray55") + 
  scale_fill_brewer(palette = "Set1", 
                    labels = short_to_display_bcg, 
                    name = "BCG") + 
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank(), 
        legend.title = element_blank(), 
        legend.position = "bottom") + 
  labs(x = "BCG status", y = "hladr") + 
  facet_wrap(~pop, ncol = 2, scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
  scale_y_continuous(trans = trans_asinh)
```

### Confounders

#### Continuous

##### Response against variable

Nothing striking.

```{r }
data_plot_hladr_infant_cont <- data_mod_hladr_infant %>%
  dplyr::select(-(age:sex)) %>%
  tidyr::pivot_longer(
    gest_age:visit_age, 
    names_to = "conf_cont", 
    values_to = "value"
  )
p_cont <- ggplot(
  data_plot_hladr_infant_cont, 
  aes(x = value, y = hladr)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_point() +
  geom_smooth(method = "loess", formula = y ~ x) +
  facet_grid(pop ~ conf_cont, 
             scales = "free", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
  theme(strip.background = element_blank()) +
  scale_colour_brewer(palette = "Dark2", 
                      labels = short_to_display_bcg) +
  labs(x = "Value", y = "hladr") +
  theme(legend.title = element_blank()) +
  geom_hline(yintercept = 0)

path_fig_rel_pdf <- file.path(
  dir_fig_vec_rel["manu_n_exp"], 
  "fig_3-p-infant-resp_vs_conf_cont.pdf"
)
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_cont, 
  height = 20, 
  width = 20, 
  units = "cm"
)
path_fig_rel_png <- file.path(
  dir_fig_vec_rel["manu_n_exp"], 
  "fig_3-p-infant-resp_vs_conf_cont.png"
)
cowplot::ggsave2(
  path_fig_rel_png, 
  p_cont, 
  height = 20, 
  width = 20, 
  units = "cm"
)
```

```{r , results = "asis"}
knitr::include_graphics(path_fig_rel)
```

##### Variable by BCG status

BCG papers appear slightly longer with slightly higher gestational ages, and are possibly heavier.

```{r }
ggplot(
  data_plot_hladr_infant_cont %>%
    dplyr::group_by(conf_cont) %>%
    dplyr::mutate(value = (value - mean(value, na.rm = TRUE)) / sd(value, na.rm = TRUE)) %>%
    dplyr::ungroup(), 
  aes(x = value, col = bcg)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
   geom_histogram(position = "dodge") +
  geom_density(bw = 0.4) +
  facet_wrap( ~ conf_cont, 
             ncol = 3, 
             scales = "free",
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
    scale_colour_brewer(palette = "Dark2", 
                      labels = short_to_display_bcg) +
    labs(x = "Standardised value", y = "Density") +
  theme(strip.background = element_blank()) +
    theme(legend.title = element_blank())
```

### Categorical

##### Response against variable

###### Race

Moderate race effect, perhaps, for CD4 T cells. 

```{r }
ggplot(
  data_mod_hladr_infant, 
  aes(x = bcg, y = hladr, fill = race, col = race)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_jitter(position = "dodge") +
  geom_boxplot(
    position = "dodge", 
    col = "black", 
    outlier.size = -1
  ) +
  facet_wrap(~pop, 
             ncol = 4, 
             scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont))  +
  scale_fill_brewer(palette = "Set1", 
                    name = "Race") +
  scale_colour_brewer(palette = "Set1", 
                      name = "Race") +
  scale_x_discrete(labels = short_to_display_bcg) +
  labs(x = "BCG status", y = "hladr")
```

###### Gender

Gender effects less strong. Treatment effect in opposite direction between females and females for NKT cells (but likely insignificant for both groups).

```{r }
ggplot(
  data_mod_hladr_infant %>%
    dplyr::mutate(sex = ifelse(is.na(sex), "unknown", sex)), 
  aes(x = bcg, y = hladr, fill = sex, col = sex)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_jitter(position = "dodge") +
  geom_boxplot(
    position = "dodge", 
    col = "black", 
    outlier.size = -1
  ) +
  facet_wrap(~pop, 
             ncol = 4, 
             scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop,
               sex = short_to_display_sex
             ))  +
  scale_fill_brewer(palette = "Set2", 
                    name = "Sex",
                    labels = short_to_display_sex) +
  scale_colour_brewer(palette = "Set2", 
                      name = "Sex",
                      labels = short_to_display_sex)
```

## Analysis

### Effect of BCG

#### Calculation

```{r , eval = TRUE, include = FALSE}
pop_vec <- unique(data_mod_hladr_infant$pop) %>%
  setdiff("cd4_ifng")
pop <- "mait"
conf_vec_infant <- c(
  "none" = "", 
  "pre_specified" = "+ sex + race"#, 
  # "data_specified" = " + ethnicity + length + gest_age + weight"
  )
results_tbl_fig3_std <- purrr::map_df(pop_vec, function(pop) {
  print(pop)
  data_mod <- data_mod_hladr_infant %>%
    dplyr::filter(pop == .env$pop)
  
  purrr::map_df(seq_along(conf_vec_infant), function(i) {
    print(names(conf_vec_infant)[i])
    # effect size
    
    trans_resp <- switch(
      pop, 
      "nkt" = trans_sqrt$transform,
      trans_asinh$transform
    )
    
    data_mod <- data_mod %>%
      dplyr::mutate(
        hladr = trans_resp(hladr)
      )
    
    trans_inv <- switch(
      pop,
      "nkt" = trans_sqrt$inverse,
      sinh
    )

    data_mod <- data_mod %>%
      dplyr::mutate(
        bcg = factor(
          bcg, 
          levels = c("no bcg", "bcg")
        )
      )
    fml_txt_base <- "hladr ~ 1"
    fml_txt_null <- paste0(fml_txt_base, conf_vec_infant[i])
    fml_txt_trt <- paste0(fml_txt_null, " + bcg")
    fml_null <- eval(parse(text = fml_txt_null))
    fml_trt <- eval(parse(text = fml_txt_trt))
    data_mod <- data_mod %>%
      dplyr::mutate(
        race = factor(race, 
                      levels = c("coloured", "black"))
        )
    fit_large <- try(quantreg::rq(
      fml_trt, 
      tau = 0.5,
      data = data_mod
    ), silent = TRUE)
    fit_small <- try(quantreg::rq(
      fml_null, 
      tau = 0.5,
      data = data_mod
    ), silent = TRUE)
    
    mod_summ <- summary(fit_large, se = "rank")
    
    sd_resid <- sd(resid(mod_summ))
    
    coef_tbl <- coefficients(mod_summ) 
    ind_bcg <- which(rownames(coef_tbl) == "bcgbcg")
    coef_vec <- coef_tbl[ind_bcg, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[ind_bcg, "coefficients"]
    
    out_tbl <- tibble::tibble(
      pop = pop,
      age = "infant",
      conf = names(conf_vec_infant)[i]
    )
    
    if(class(fit_large)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est = coef_est, 
          diff_lb = coef_vec[1], 
          diff_ub = coef_vec[2], 
          sd_resid_large = sd(resid(mod_summ))
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est = NA, 
          diff_lb = NA, 
          diff_ub = NA, 
          sd_resid_large = NA
        )
    }
    
    if(class(fit_small)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          sd_resid_small = sd(resid(summary(fit_small)))
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          sd_resid_small = NA
        )
    }
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        sd_raw_overall = sd(data_mod$hladr), 
        sd_raw_grp_mean = purrr::map_dbl(unique(data_mod$bcg), function(x) {
          data_mod_bcg <- data_mod %>%
            dplyr::filter(bcg == x)
          sd(data_mod_bcg$hladr)
        }) %>% 
          mean()
      )
    
    if(class(fit_large)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_large = coef_est / sd_resid_large, 
          diff_lb_std_resid_large = diff_lb / sd_resid_large, 
          diff_ub_std_resid_large = diff_ub / sd_resid_large
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_large = NA, 
          diff_lb_std_resid_large = NA, 
          diff_ub_std_resid_large = NA
        )
    }
    if(class(fit_small)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_small = coef_est / sd_resid_small, 
          diff_lb_std_resid_small = diff_lb / sd_resid_small, 
          diff_ub_std_resid_small = diff_ub / sd_resid_small
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_small = NA, 
          diff_lb_std_resid_small = NA, 
          diff_ub_std_resid_small = NA
        )
    }
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        diff_est_std_raw_overall = coef_est / sd_raw_overall, 
        diff_lb_std_raw_overall = diff_lb / sd_raw_overall, 
        diff_ub_std_raw_overall = diff_ub / sd_raw_overall
      ) %>%
      dplyr::mutate(
        diff_est_std_raw_grp_mean = coef_est / sd_raw_grp_mean, 
        diff_lb_std_raw_grp_mean = diff_lb / sd_raw_grp_mean, 
        diff_ub_std_raw_grp_mean = diff_ub / sd_raw_grp_mean
      )
    

    if(class(fit_large)[1] != "try-error" && 
       class(fit_small)[1] != "try-error") {
      anova_fit <- anova(fit_large, fit_small)
      p = anova_fit$table$pvalue
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_p = p
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_p = NA
        )
      }

    # Group-wise confidence intervals
    # ================================
    
    # no bcg
    
    coef_tbl <- coefficients(mod_summ) 
    ind_int <- which(rownames(coef_tbl) == "(Intercept)")
    coef_vec_est <- coef_tbl[ind_int, "coefficients"]
    coef_vec_int_ctrl <- coef_tbl[ind_int, c("lower bd", "upper bd")] %>%
      as.vector()
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        ctrl_grp_est = coef_vec_est,
        ctrl_grp_lb = coef_vec_int_ctrl[1],
        ctrl_grp_ub = coef_vec_int_ctrl[2]
      )
    
    data_mod_trt <- data_mod %>%
      dplyr::mutate(
        bcg = factor(
          bcg, 
          levels = c("bcg", "no bcg")
        )
      )

    fit_large_trt <- try(quantreg::rq(
      fml_trt, 
      tau = 0.5,
      data = data_mod_trt
    ), silent = TRUE)

    mod_summ_trt <- summary(fit_large_trt)

    coef_tbl <- coefficients(mod_summ_trt) 
    ind_int <- which(rownames(coef_tbl) == "(Intercept)")
    coef_vec_est_trt <- coef_tbl[ind_int, "coefficients"]
    coef_vec_int_trt <- coef_tbl[ind_int, c("lower bd", "upper bd")] %>%
      as.vector()
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        trt_grp_est = coef_vec_est_trt,
        trt_grp_lb = coef_vec_int_trt[1],
        trt_grp_ub = coef_vec_int_trt[2]
      )
    
    # transform CI's back to original scale
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        ctrl_grp_est = trans_inv(ctrl_grp_est),
        ctrl_grp_lb = trans_inv(ctrl_grp_lb),
        ctrl_grp_ub = trans_inv(ctrl_grp_ub),
        trt_grp_est = trans_inv(trt_grp_est),
        trt_grp_lb = trans_inv(trt_grp_lb),
        trt_grp_ub = trans_inv(trt_grp_ub)
      )
    
    out_tbl
  })
})
```

```{r }
results_tbl_fig3_cyt <- purrr::map_df(c("cd4"), function(pop) {
  print(pop)
  data_mod <- data_mod_hladr_infant %>%
    dplyr::filter(pop == .env$pop) %>%
    dplyr::filter(bcg == "bcg")
  
  data_mod <- data_mod %>%
    dplyr::bind_rows(data_mod_hladr_infant_cyt)
  purrr::map_df(seq_along(conf_vec_infant), function(i) {
    print(names(conf_vec_infant)[i])
    # effect size
    
    trans_resp <- switch(
      pop, 
      "nkt" = trans_sqrt$transform,
      trans_asinh$transform
    )
    
    data_mod <- data_mod %>%
      dplyr::mutate(
        hladr = trans_resp(hladr)
      )
    
    trans_inv <- switch(
      pop,
      "nkt" = trans_sqrt$inverse,
      sinh
    )

    data_mod <- data_mod %>%
      dplyr::mutate(
        pop = factor(
          pop, 
          levels = c("cd4", "cd4_ifng")
        ),
        race = factor(race, 
                      levels = c("coloured", "black")), 
        sex = factor(sex,
                     levels = c("female", "male"))
      )
    fml_txt_base <- "hladr ~ 1"
    fml_txt_null <- paste0(fml_txt_base, conf_vec_infant[i])
    fml_txt_trt <- paste0(fml_txt_null, " + pop")
    fml_null <- eval(parse(text = fml_txt_null))
    fml_trt <- eval(parse(text = fml_txt_trt))

    fit_large <- try(quantreg::rq(
      fml_trt, 
      tau = 0.5,
      data = data_mod
    ), silent = TRUE)
    fit_small <- try(quantreg::rq(
      fml_null, 
      tau = 0.5,
      data = data_mod
    ), silent = TRUE)
    
    mod_summ <- summary(fit_large, se = "rank")
    
    sd_resid <- sd(resid(mod_summ))
    
    coef_tbl <- coefficients(mod_summ) 
    ind_cd4_ifng <- which(rownames(coef_tbl) == "popcd4_ifng")
    coef_vec <- coef_tbl[ind_cd4_ifng, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[ind_cd4_ifng, "coefficients"]
    
    out_tbl <- tibble::tibble(
      pop = pop,
      age = "infant",
      conf = names(conf_vec_infant)[i]
    )
    
    if(class(fit_large)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est = coef_est, 
          diff_lb = coef_vec[1], 
          diff_ub = coef_vec[2], 
          sd_resid_large = sd(resid(mod_summ))
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est = NA, 
          diff_lb = NA, 
          diff_ub = NA, 
          sd_resid_large = NA
        )
    }
    
    if(class(fit_small)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          sd_resid_small = sd(resid(summary(fit_small)))
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          sd_resid_small = NA
        )
    }
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        sd_raw_overall = sd(data_mod$hladr), 
        sd_raw_grp_mean = purrr::map_dbl(unique(data_mod$bcg), function(x) {
          data_mod_bcg <- data_mod %>%
            dplyr::filter(bcg == x)
          sd(data_mod_bcg$hladr)
        }) %>% 
          mean()
      )
    
    if(class(fit_large)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_large = coef_est / sd_resid_large, 
          diff_lb_std_resid_large = diff_lb / sd_resid_large, 
          diff_ub_std_resid_large = diff_ub / sd_resid_large
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_large = NA, 
          diff_lb_std_resid_large = NA, 
          diff_ub_std_resid_large = NA
        )
    }
    if(class(fit_small)[1] != "try-error") {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_small = coef_est / sd_resid_small, 
          diff_lb_std_resid_small = diff_lb / sd_resid_small, 
          diff_ub_std_resid_small = diff_ub / sd_resid_small
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_est_std_resid_small = NA, 
          diff_lb_std_resid_small = NA, 
          diff_ub_std_resid_small = NA
        )
    }
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        diff_est_std_raw_overall = coef_est / sd_raw_overall, 
        diff_lb_std_raw_overall = diff_lb / sd_raw_overall, 
        diff_ub_std_raw_overall = diff_ub / sd_raw_overall
      ) %>%
      dplyr::mutate(
        diff_est_std_raw_grp_mean = coef_est / sd_raw_grp_mean, 
        diff_lb_std_raw_grp_mean = diff_lb / sd_raw_grp_mean, 
        diff_ub_std_raw_grp_mean = diff_ub / sd_raw_grp_mean
      )
    

    if(class(fit_large)[1] != "try-error" && 
       class(fit_small)[1] != "try-error") {
      anova_fit <- anova(fit_large, fit_small)
      p = anova_fit$table$pvalue
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_p = p
        )
    } else {
      out_tbl <- out_tbl %>%
        dplyr::mutate(
          diff_p = NA
        )
    }
    
    data_mod_wsc <- data_mod %>%
      tidyr::pivot_wider(
        names_from = "pop", 
        values_from = "hladr"
      )  %>%
      dplyr::filter(!(is.na(cd4) | is.na(cd4_ifng)))
    
    wsc_test <- wilcox.test(
      x = data_mod_wsc$cd4_ifng, 
      y = data_mod_wsc$cd4,
      paired = TRUE, 
      conf.int = TRUE
    )
    diff_p_wsc <- wsc_test$p.value[[1]]
    diff_est_wsc <- wsc_test$estimate[[1]]
    diff_lb_wsc <- wsc_test$conf.int[[1]]
    diff_ub_wsc <- wsc_test$conf.int[[2]]
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        diff_est_wsc = diff_est_wsc, 
        diff_lb_wsc = diff_lb_wsc, 
        diff_ub_wsc = diff_ub_wsc, 
        diff_p_wsc = diff_p_wsc
      )

    # Group-wise confidence intervals
    # ================================
    
    # no bcg
    
    coef_tbl <- coefficients(mod_summ) 
    ind_int <- which(rownames(coef_tbl) == "(Intercept)")
    coef_vec_est <- coef_tbl[ind_int, "coefficients"]
    coef_vec_int_ctrl <- coef_tbl[ind_int, c("lower bd", "upper bd")] %>%
      as.vector()
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        ctrl_grp_est = coef_vec_est,
        ctrl_grp_lb = coef_vec_int_ctrl[1],
        ctrl_grp_ub = coef_vec_int_ctrl[2]
      )
    
    data_mod_trt <- data_mod %>%
      dplyr::mutate(
        pop = factor(
          pop, 
          levels = c("cd4_ifng", "cd4")
        )
      )

    fit_large_trt <- try(quantreg::rq(
      fml_trt, 
      tau = 0.5,
      data = data_mod_trt
    ), silent = TRUE)

    mod_summ_trt <- summary(fit_large_trt)

    coef_tbl <- coefficients(mod_summ_trt) 
    ind_int <- which(rownames(coef_tbl) == "(Intercept)")
    coef_vec_est_trt <- coef_tbl[ind_int, "coefficients"]
    coef_vec_int_trt <- coef_tbl[ind_int, c("lower bd", "upper bd")] %>%
      as.vector()
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        trt_grp_est = coef_vec_est_trt,
        trt_grp_lb = coef_vec_int_trt[1],
        trt_grp_ub = coef_vec_int_trt[2]
      )
    
    # transform CI's back to original scale
    
    out_tbl <- out_tbl %>%
      dplyr::mutate(
        ctrl_grp_est = trans_inv(ctrl_grp_est),
        ctrl_grp_lb = trans_inv(ctrl_grp_lb),
        ctrl_grp_ub = trans_inv(ctrl_grp_ub),
        trt_grp_est = trans_inv(trt_grp_est),
        trt_grp_lb = trans_inv(trt_grp_lb),
        trt_grp_ub = trans_inv(trt_grp_ub)
      )
    
    out_tbl
  })
})
```

#### Effect of BCG in infants

```{r , results = "asis"}
results_tbl_fig3_std %>%
  dplyr::filter(conf == "pre_specified") %>%
  dplyr::select(pop, age, diff_est, diff_p) %>%
  dplyr::mutate(pop = short_to_long_pop[pop]) %>%
  dplyr::arrange(diff_p) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonf", 
                                       n = length(pop_vec) + 1)) %>%
  dplyr::rename(Pop = pop, 
                Age = age, 
                `BCG effect: est.` = `diff_est`, 
                `BCG effect: p-value` = diff_p, 
                `BCG effect: q-value (Bonf)` = diff_p_bonf) %>%
  pander::pandoc.table()
```

#### Effect of IFN$\gamma$ positivity in CD4 T cells in infants

```{r , results = "asis"}
results_tbl_fig3_cyt %>%
  dplyr::filter(conf == "pre_specified") %>%
  dplyr::select(pop, age, diff_est, diff_p) %>%
  dplyr::mutate(pop = short_to_long_pop[pop]) %>%
  dplyr::arrange(diff_p) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonf", n = length(pop_vec) + 1)) %>%
  dplyr::rename(Pop = pop, 
                Age = age, 
                `IFNg+ effect: est.` = `diff_est`, 
                `IFNg+ effect: p-value` = diff_p, 
                `IFNg+ effect: q-value (Bonf)` = diff_p_bonf) %>%
  pander::pandoc.table()
```

#### Plotting

```{r }
pop_to_lab_hladr_infant <- c(
  "mait" = bquote(paste(plain(paste("CD3+ MAIT cells (MFI)")))), 
  "nkt" = bquote(paste(plain(paste("CD3+ NKT cells (MFI)")))),
  "cd1b" = bquote(paste(plain(paste("CD3+ GMM T cells (MFI)")))),
  "gd" = bquote(paste(plain(paste("CD3+ ")), gamma, delta, plain(paste("TCR+ cells (MFI)")))),                     
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (MFI)"))))
)

pop_to_lab_hladr_infant_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG")))), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta, plain(paste(" BCG"))))
)
```

```{r , include = FALSE}
plot_list_fig3 <- get_fig_3_sub_plots()

plot_list_align <- purrr::map(seq_along(plot_list_fig3), function(i) {
  list(ggplot() + geom_blank() + theme_void(), 
       plot_list_fig3[[i]]$p_grp,
       ggplot() + geom_blank() + theme_void())
})

p_fig3_grp <- cowplot::plot_grid(
  plotlist = plot_list_align %>%
    purrr::flatten(), 
  ncol = 6,
  rel_widths = c(0.1, 2, 1, 0.1, 2, 1), 
  align = "hv", 
  axis = "lrtb"
  #labels = LETTERS[1:7],
  #hjust = -0.175
)

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_3-grp.pdf"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig3_grp, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)

p_fig3 <- p_fig3_grp
x_vec <- rep(c(2/6, 5/6), 3)
nudge_y_diff <- 0.0115# 0.032
y_vec <- rep(1 - 1/3 * 1:3, each = 2) + nudge_y_diff
y_vec[2:6] <- y_vec[2:6] + 0.0105
for(i in seq_along(plot_list_fig3)) {
  p_fig3 <- p_fig3 +
    cowplot::draw_plot(
      plot_list_fig3[[i]]$p_diff, 
      width = 1/6, 
      height = 1/3 - nudge_y_diff - 0.0105, 
      x = x_vec[i], 
      y = y_vec[i]
    ) 
}

x_vec_hladr <- rep(c(0.02, 0.52), 3)
y_vec_hladr <- rep(0.5, 6)
nudge_down <- 0.0125
p_fig3 <- p_fig3 + 
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.03, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.5175, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.03, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.505, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
    text = "HLADR+", 
    x = 0.02, 
    y = 0.2167 - nudge_down, 
    angle = 90, 
    hjust = 0.5, 
    vjust = 0.5
  ) 

p_fig3 <- p_fig3 + 
 cowplot::draw_label(
    label = bquote(paste(plain(paste("IFN")), gamma, "+")),
    angle = 45, 
    x = 0.2935, 
    y = 0.72,
    size = 12
  )


path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_3.pdf"
  )
path_fig_rel_png <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_3.png"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig3, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
od(path_fig_rel_pdf)
cowplot::ggsave2(
  path_fig_rel_png, 
  p_fig3, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
```

```{r , results = "asis"}
knitr::include_graphics(path_fig_rel_png)
```

