# Figure 4

Same as Figure 2. 

## Relevant criticisms

## Proposed approach

## Data exploration

```{r }
data_tidy_hladr_adult <- DataTidyGelaDURT::data_tidy_hladr_adult %>%
  tibble::as_tibble()

data_mod_hladr_adult <- data_tidy_hladr_adult %>%
  dplyr::left_join(
    data_tidy_clin_adult, 
    by = "pid"
  ) %>%
  dplyr::rename(hladr = hladr_mfi) %>%
  dplyr::mutate(
  days = factor(
    days, 
    levels = as.character(c(0, 21, 35, 365))
  ), 
  pop = factor(pop, 
               levels = c(
                 "cd4",
                 "mait", 
                 "nkt", "cd1b", 
                 "gd"
               ))
  ) %>%
  dplyr::mutate(
    day_type = ifelse(days == "0", "pre_bcg", "post_bcg")
  ) %>%
  dplyr::mutate(
    hladr = pmax(hladr, 0)
  ) %>%
  dplyr::mutate(
    race = factor(race, 
              levels = c("non_black", "black")), 
    sex = factor(
      sex, 
      levels = c("female", "male")
    )
  )
```

```{r }
pop_to_lab_hladr <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (MFI)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (MFI)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM+ T cells (MFI)")))),
  "gem" = bquote(paste(plain(paste("GEM T cells (MFI)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste("TCR+ cells (MFI)")))), 
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (MFI)")))), 
  "cd4_ifng" = bquote(paste(plain(paste("IFN")), gamma, plain(paste("+CD4+ T cells (MFI)"))))
)

pop_to_lab_hladr_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

### Response against BCG status

Square root or asinh transformation may help for tcrgd and cd1, but seems less help for cd4, nkt and maits. May consider pulling that enormous tcrgd value in. Should probably use a gamma dbn for  cd1b (asinh scale) and tcrgd (square root scale - else very large negative obs). NKTs, CD4s and MAITs could probably simply use a normal dbn. 

#### Identity (no) transformation

```{r }
ggplot(data_mod_hladr_adult, 
       aes(x = days, y = hladr, fill = day_type)) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_boxplot(outlier.size = 1, 
               outlier.colour = "gray55") + 
  guides(fill = "none") + 
  theme(legend.title = element_blank(), 
        legend.position = "bottom") + 
  labs(x = "Days since revaccination", y = "hladr") + 
  facet_wrap(~pop, ncol = 2, scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
  scale_y_continuous(trans = "identity")
```

#### Square root transformation

```{r }
ggplot(data_mod_hladr_adult, 
       aes(x = days, y = hladr, fill = day_type)) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_boxplot(outlier.size = 1, 
               outlier.colour = "gray55") + 
  guides(fill = "none") + 
  theme(legend.title = element_blank(), 
        legend.position = "bottom") + 
  labs(x = "Days since revaccination", y = "hladr") + 
  facet_wrap(~pop, ncol = 2, scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
  scale_y_continuous(trans = "sqrt")
```

#### Asinh transformation

```{r }
trans_asinh <- scales::trans_new(
  name = "asinh", 
  transform = asinh, 
  inverse = sinh
)
trans_sqrt <- scales::trans_new(
  name = "sqrt_custom", 
  transform = sqrt, 
  inverse = function(x) x^2
)
ggplot(data_mod_hladr_adult, 
       aes(x = days, y = hladr, fill = day_type)) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "y") +
  geom_boxplot(outlier.size = 1, 
               outlier.colour = "gray55") + 
  guides(fill = "none") + 
  theme(legend.title = element_blank(), 
        legend.position = "bottom") + 
  labs(x = "Days since revaccination", y = "hladr") + 
  facet_wrap(~pop, ncol = 2, scales = "free_y", 
             labeller = labeller(
               pop = short_to_long_pop, 
               conf_cont = short_to_long_var_cont)) +
  scale_y_continuous(trans = trans_asinh)
```

```{r }
get_trans_obj <- function(x) {
  switch(
    x, 
    "cd4" = ,
    "mait" = ,
    "nkt" = scales::identity_trans(),
    "cd1b" = trans_asinh, 
    "gd" = scales::sqrt_trans()
  )
}
get_trans <- function(x) {
  get_trans_obj(x)$transform
}

get_trans_inv <- function(x) {
  get_trans_obj(x)$inverse
}
```

## Analysis

### Effect of BCG

#### Calculation

```{r , eval = TRUE, include = FALSE}
pop_vec <- unique(data_mod_hladr_adult$pop) %>%
  setdiff("cd4_ifng")
pop <- "cd1b"
conf_vec_adult <- c(
  "none" = "", 
  "pre_specified" = "+ sex + race" 
  )
results_tbl_fig4_std <- purrr::map_df(pop_vec, function(pop) {
  print(pop)
  data_mod <- data_mod_hladr_adult %>%
    dplyr::filter(pop == .env$pop)
  
  trans_resp <- get_trans(pop)
  trans_inv <- get_trans_inv(pop)
  
  data_mod <- data_mod %>%
    dplyr::mutate(
      hladr = trans_resp(hladr)
    )
  
  # calculate residual standard deviation
  fit_large <- try(quantreg::rq(
    hladr ~ 1 + days + sex + race, 
    tau = 0.5,
    data = data_mod
  ), silent = TRUE)
  
  out_tbl <- tibble::tibble(
    pop = pop,
    age = "adult"
  ) %>%
    dplyr::mutate(
      sd_std = sd(resid(summary(fit_large, se = "rank")))
    )
  
  day_vec <- c("any", "0", "21", "35", "365")
  results_tbl_day <- purrr::map_df(day_vec, function(day) {
    
    if (day == "any") {
      
      make_pos_strict <- function(x) {
        range_x <- diff(range(x, na.rm = TRUE))
        diff_x <- range_x * 0.01
        min_x <-  min(diff_x, min(x[x > 0], na.rm = TRUE),
                      na.rm = TRUE)
        pmax(min_x, x)
        }
      
      data_mod_mm <- switch(
        pop, 
        "cd1b" = ,
        "gd" = {
          data_mod %>%
            dplyr::mutate(
              hladr = make_pos_strict(hladr)
            )
        }, 
        data_mod
      )
      
      mod_family <- switch(
        pop, 
        "cd1b" = ,
        "gd" = {
          Gamma(link = "log")
        }, 
        gaussian(link = "identity")
      )
      
      # overall p-value
      fit_large_overall <- glmmTMB::glmmTMB(
         hladr ~ 1 + days + sex + race, 
        data = data_mod_mm, 
        family = mod_family
      )
      fit_small_overall <- glmmTMB::glmmTMB(
         hladr ~ 1 + sex + race, 
        data = data_mod_mm, 
        family = mod_family
      )
      diff_p_overall_mm <- modutils:::.test_lr(
        mod_large = fit_large_overall, 
        mod_small = fit_small_overall
      )$p
      
      diff_p_overall_kw <- kruskal.test(
        x = data_mod$hladr, 
        g = data_mod$days
      )$p.value
      
      out_tbl <- tibble::tibble(
        day = day,
        est = NA, 
        lb = NA,
        ub = NA,
        diff_p = diff_p_overall_mm, 
        diff_est = NA, 
        diff_lb = NA, 
        diff_ub = NA
      )
      return(out_tbl)
    }
    
    # test for effect
    if (day != "0") {
      data_mod_wsc <- data_mod %>%
        dplyr::filter(days %in% c("0", day)) %>%
        dplyr::select(pid, days, hladr) %>%
         tidyr::pivot_wider(
          names_from = "days", 
          values_from = "hladr"
        )  
      wsc_test <- wilcox.test(
        x = data_mod_wsc[[day]],
        y = data_mod_wsc[["0"]], 
        paired = TRUE, 
        conf.int = TRUE
      )
      diff_p_wsc <- wsc_test$p.value[[1]]
      diff_est_wsc <- wsc_test$estimate[[1]]
      diff_lb_wsc <- wsc_test$conf.int[[1]]
      diff_ub_wsc <- wsc_test$conf.int[[2]]  
    } else {
      diff_p_wsc <- NA
      diff_est_wsc <- NA
      diff_lb_wsc <- NA
      diff_ub_wsc <- NA
    }
    
    extra_day <- ifelse(day == "0", "21", "0")
    fit_day <- try(quantreg::rq(
      hladr ~ 1 + days + sex + race,
      tau = 0.5,
      data = data_mod %>%
        dplyr::filter(days %in% c(extra_day, day)) %>%
        dplyr::select(sex, race, hladr, days) %>%
        dplyr::mutate(days = factor(
          days, 
          levels = c(
            day, 
            extra_day
          )
        ))
      ), silent = TRUE)
    
    mod_summ <- summary(fit_day, se = "rank")
  
    coef_tbl <- coefficients(mod_summ)
    coef_vec <- coef_tbl[1, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[1, "coefficients"]
    
    tibble::tibble(
      day = day,
      est = coef_est, 
      lb = coef_vec[1], 
      ub = coef_vec[2], 
      diff_p = diff_p_wsc, 
      diff_est = diff_est_wsc, 
      diff_lb = diff_lb_wsc, 
      diff_ub = diff_ub_wsc
      )
  }) %>%
    dplyr::mutate(
      diff_est_std = diff_est / out_tbl$sd_std, 
      diff_lb_std = diff_lb / out_tbl$sd_std, 
      diff_ub_std = diff_ub / out_tbl$sd_std
    )
  
  out_tbl <- out_tbl %>%
    dplyr::bind_cols(
      results_tbl_day
    )

  # transform CI's back to original scale
  
  out_tbl <- out_tbl %>%
    dplyr::mutate(
      est = trans_inv(est),
      lb = trans_inv(lb),
      ub = trans_inv(ub)
    )
  
  out_tbl
}) %>%
  dplyr::group_by(
    day
  ) %>%
  dplyr::mutate(
    diff_p_bonf = p.adjust(diff_p, method = "bonferroni")
  )
```

#### Effect of BCG by any day

```{r , results = "asis"}
results_tbl_fig4_std %>%
  dplyr::filter(day == "any") %>%
  dplyr::select(pop, age, diff_p) %>%
  dplyr::mutate(pop = short_to_long_pop[pop]) %>%
  dplyr::arrange(diff_p) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonf")) %>%
  dplyr::rename(Pop = pop, 
                Age = age, 
                `BCG effect: p-value` = diff_p, 
                `BCG effect: q-value (Bonf)` = diff_p_bonf) %>%
  pander::pandoc.table() 
```

#### Effect of BCG for individual days

```{r , results = "asis"}
results_tbl_fig4_std %>%
  dplyr::filter(!day %in% c("any", "0")) %>%
  dplyr::group_by(day) %>%
  dplyr::select(pop, age, day, diff_est, diff_p) %>%
  dplyr::mutate(pop = short_to_long_pop[pop]) %>%
  dplyr::arrange(diff_p) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonf")) %>%
  dplyr::ungroup() %>%
  dplyr::rename(Pop = pop, 
                Age = age, 
                `BCG effect: p-value` = diff_p, 
                `BCG effect: q-value (Bonf)` = diff_p_bonf) %>%
  pander::pandoc.table()
```

#### Plotting

```{r }
pop_to_lab_hladr_adult <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (MFI)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (MFI)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM T cells (MFI)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste(" T cells (MFI)")))),                     
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (MFI)"))))
)

pop_to_lab_hladr_adult_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc"))))), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta, paste(plain(paste("vs pre-vacc")))))
)
```

```{r , include = FALSE}
plot_list_fig4 <- get_fig_4_sub_plots()

plot_list_align <- purrr::map(seq_along(plot_list_fig4), function(i) {
  list(ggplot() + geom_blank() + theme_void(), 
       plot_list_fig4[[i]]$p_grp,
       ggplot() + geom_blank() + theme_void())
})

p_fig4_grp <- cowplot::plot_grid(
  plotlist = plot_list_align %>%
    purrr::flatten(), 
  ncol = 6,
  rel_widths = c(0.15, 2, 1, 0.15, 2, 1), 
  align = "hv", 
  axis = "lrtb"
)

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_4-grp.pdf"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig4_grp, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
od(path_fig_rel_pdf)

p_fig4_diff <- p_fig4_grp
nudge_y_diff <- 0
y_vec <- rep(1 - 1/3 * 1:3, each = 2) + nudge_y_diff

for(i in seq_along(plot_list_fig4)) {
  p_fig4_diff <- p_fig4_diff +
    cowplot::draw_plot(
      plot_list_fig4[[i]]$p_diff, 
      width = 1/6, 
      height = 1/3 - nudge_y_diff - 0.0105, 
      x = x_vec[i], 
      y = y_vec[i]
    ) 
}

x_vec_hladr <- rep(c(0.02, 0.52), 3)
y_vec_hladr <- rep(0.5, 6)
nudge_down <- 0.0125
p_fig4_diff <- p_fig4_diff + 
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.03, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.54, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.0175, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.5275, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
    text = "HLADR+", 
    x = 0.036375, 
    y = 0.2167 - nudge_down, 
    angle = 90, 
    hjust = 0.5, 
    vjust = 0.5
  ) 

plot_tbl_legend <- tibble::tibble(
  x = c(0.5, 0.5), 
  y = c(0.6, 0.5), 
  col = c("red", "dodgerblue"), 
  shape = c("circle"), 
  lbl = c("Pre-BCG", "Post-BCG")
)

p_legend <- ggplot(plot_tbl_legend) + 
  theme_void() + 
  geom_point(aes(x, y, col = col), 
             show.legend = FALSE, 
             size = 2, alpha = 0.5) +
  lims(x = 0:1, y = 0:1) +
  geom_text(aes(x = x + 0.05, y, label = lbl), 
            hjust = 0, size = 4.25) +
  scale_colour_manual(
    values = c(
      "red" = "red", 
      "dodgerblue" = "dodgerblue"
    )
  )
p_fig4 <- p_fig4_diff + 
  cowplot::draw_plot(
    plot = p_legend, 
    y = 0, 
    x = 1/2, 
    width = 1/2, 
    height = 1/4
  )
  

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_4.pdf"
  )
path_fig_rel_png <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_4.png"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig4, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
od(path_fig_rel_pdf)
cowplot::ggsave2(
  path_fig_rel_png, 
  p_fig4, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
```
