# Figure 6

## Relevant criticisms

## Proposed approach

## Data exploration

```{r }
data_raw_fig6 <- DataTidyGelaDURT::data_tidy_mem_infant %>%
  dplyr::rename(
    grp = bcg
  ) %>%
  dplyr::bind_rows(
    DataTidyGelaDURT::data_tidy_mem_adult %>%
      dplyr::rename(
        grp = day
      ) %>%
      dplyr::mutate(
        grp = paste0("day_", grp)
      ) %>%
      dplyr::filter(
        grp %in% c("day_0", "day_365")
      )
  )


pop_vec <- c("mait", "nkt", "gd", "cd4")
pop_sub_vec <- c(
  "CD45RA+CCR7+", "CD45RA-CCR7+", "CD45RA-CCR7-", "CD45RA+CCR7-" 
)
data_raw_fig6 <- data_raw_fig6 %>%
  dplyr::mutate(
    pop = factor(
      pop, 
      levels = pop_vec
    ), 
    pop_sub = factor(
      pop_sub, 
      levels = pop_sub_vec
    )
  ) %>%
  dplyr::mutate(
    grp = factor(
      grp, 
      levels = c(
        "no bcg", 
        "bcg", 
        "day_0", 
        "day_365"
      )
    )
  )
data_tidy_clin <- data_tidy_clin_adult %>%
  dplyr::select(pid, race, sex) %>%
  dplyr::bind_rows(
    data_tidy_clin_infant %>%
      dplyr::select(pid, race, sex) %>%
      dplyr::mutate(race = ifelse(race == "coloured", "non_black", race))
  )

data_tidy_fig6 <- data_raw_fig6 %>%
  dplyr::left_join(
    data_tidy_clin, 
    by = "pid"
  ) %>%
  dplyr::mutate(
    race = factor(race, 
              levels = c("non_black", "black")), 
    sex = factor(
      sex, 
      levels = c("female", "male")
    )
  )

data_tidy_fig6 <- data_tidy_fig6 %>%
  dplyr::mutate(
    x_order = paste0(pop_sub, "_", grp)
  ) %>%
  dplyr::arrange(
    pop, pop_sub, grp
  )

chr_to_num_x_order <- setNames(
  seq_along(unique(data_tidy_fig6$x_order)), 
  unique(data_tidy_fig6$x_order)
)
data_tidy_fig6 <- data_tidy_fig6 %>%
  dplyr::mutate(
    x_order_num = chr_to_num_x_order[x_order]
  ) %>%
  dplyr::mutate(
    pop_x_order = paste0(pop, "_", x_order), 
    pop_pop_sub = paste0(pop, "_", pop_sub)
  )
x_order_vec <- unique(data_tidy_fig6$x_order)
pop_x_order_vec <- unique(data_tidy_fig6$pop_x_order)
pop_pop_sub_vec <- unique(data_tidy_fig6$pop_pop_sub)
```

```{r }
pop_to_lab_mem <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (%)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (%)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM+ T cells (%)")))),
  "gem" = bquote(paste(plain(paste("GEM T cells (%)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste("TCR+ cells (%)")))), 
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (%)")))), 
  "cd4_ifng" = bquote(paste(plain(paste("IFN")), gamma, plain(paste("+CD4+ T cells (%)"))))
)

pop_to_lab_mem_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

### Identity transformation

```{r }
p <- ggplot(
  data_tidy_fig6 %>%
    dplyr::mutate(
      grp = factor(
        grp, 
        levels = c("no bcg", "bcg", "day_0", "day_365")
      )
    ), 
  aes(x = x_order, fill = pop_sub)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "xy") +
  geom_boxplot(aes(y = freq)) +
  facet_wrap(~pop, ncol = 4) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  scale_x_discrete(
    breaks = x_order_vec, 
    limits = x_order_vec
  )
for (x in unique(data_tidy_fig6$x_order)) {
  p <- p + 
    ggforce::geom_sina(aes(y = freq, shape = grp), maxwidth = 0.75, 
                       scale = "width", 
                       data = data_tidy_fig6 %>%
                         dplyr::filter(x_order == x))
}
p 
```

### Square root transformation

```{r }
p +
  scale_y_sqrt()
```

It generally seems that the square root transformation makes the data nicer to work with, as long as the median response is less than 0.75. Above that the identity transformation using the beta distribution may work better, especially for those capped at 100. In that case, the frequencies should be divided by 100 to work with proportions instead. 

## Analysis

### Calculation

```{r }
pop_pop_sub_to_trans_obj_tbl <- data_tidy_fig6 %>%
  dplyr::group_by(pop_pop_sub, grp) %>%
  dplyr::summarise(med = median(freq, na.rm = TRUE),
                   .groups = "drop_last"
                   ) %>%
  dplyr::summarise(trans = list(switch(
    as.character(any(med > 0.5)), 
    "TRUE" = scales::identity_trans(), 
    "FALSE" = scales::sqrt_trans()
  )))
pop_pop_sub_to_trans_obj <- pop_pop_sub_to_trans_obj_tbl$trans %>%
  setNames(pop_pop_sub_to_trans_obj_tbl$pop_pop_sub)
```

```{r }
pop_pop_sub <- pop_pop_sub_vec[1]
results_list_fig6 <- purrr::map(pop_pop_sub_vec, function(pop_pop_sub) {
  data_tidy_mod <- data_tidy_fig6 %>%
    dplyr::filter(pop_pop_sub == .env$pop_pop_sub) 
  
  trans_obj <- pop_pop_sub_to_trans_obj[[pop_pop_sub]]
  
  data_tidy_mod <- data_tidy_mod %>%
    dplyr::mutate(prop = freq / 1e2) %>%
    dplyr::mutate(prop = trans_obj$transform(prop))
  
  # =======================
  # get estimates and ci
  # =======================
  
  age_vec <- unique(data_tidy_mod$age)
  age <- age_vec[1]
  est_ci_tbl <- purrr::map_df(age_vec, function(age) {
    data_tidy_mod_est_ci  <- data_tidy_mod %>%
      dplyr::filter(age == .env$age)
    grp_vec <- unique(data_tidy_mod_est_ci$grp) %>%
      as.character()
    grp <- grp_vec[1] 
    purrr::map_df(grp_vec, function(grp) {
      print(grp)
      data_tidy_mod_est_ci_grp <- data_tidy_mod_est_ci %>%
        dplyr::mutate(
          grp = factor(
            grp, 
            levels = c(
              .env$grp, 
              setdiff(grp_vec, .env$grp)
            )
          )
        )
      # calculate residual standard deviation
      fit_large <- try(quantreg::rq(
        freq ~ 1 + grp + sex + race, 
        tau = 0.5,
        data = data_tidy_mod_est_ci_grp
      ), silent = TRUE)
      
      sd_std = sd(resid(summary(fit_large, se = "rank")))
      
      # calculate unadjusted eff and ci
      fit_large <- try(quantreg::rq(
        freq ~ 1 + grp, 
        tau = 0.5,
        data = data_tidy_mod_est_ci_grp
      ), silent = TRUE)
      mod_summ <- summary(fit_large, se = "rank")

      coef_tbl <- coefficients(mod_summ)
      coef_vec <- coef_tbl[1, c("lower bd", "upper bd")] %>%
        as.vector()
      coef_est <- coef_tbl[1, "coefficients"]
      
      sd_std = sd(resid(summary(fit_large, se = "rank")))
      tibble::tibble(
        pop = data_tidy_mod_est_ci_grp$pop[[1]],
        age = age, 
        pop_pop_sub = pop_pop_sub, 
        pop_sub = gsub("\\w+_", "", pop_pop_sub), 
        grp = grp, 
        sd_std = sd_std,
        est = coef_est,
        lb = coef_vec[1], 
        ub = coef_vec[2]
        ) %>%
        dplyr::mutate(
          est = trans_obj$inverse(est), 
          lb = trans_obj$inverse(lb), 
          ub = trans_obj$inverse(ub)
        )
    })
  })
  
  # =======================
  # get diff est, ci and p-value
  # =======================
  
  var_exp_vec <- c("bcg", "day_365", "adult")
  var_exp_to_lvl <- list(
    "bcg" = c("no bcg", "bcg"), 
    "day_365" = c("day_0", "day_365"), 
    "adult" = c("infant", "adult")
  )
  var_exp_to_col <- c(
    "bcg" = "grp", 
    "day_365" = "grp", 
    "adult" = "age"
  )
  var_exp <- var_exp_vec[1]
  var_exp_to_fml_trt <- list(
    "bcg" = freq ~ 1 + grp + sex + race, 
    "day_365" = freq ~ 1 + grp + sex + race,
    "adult" = freq ~ 1 + age + sex + race
  )
  var_exp_to_fml_null <- list(
    "bcg" = freq ~ 1  + sex + race, 
    "day_365" = freq ~ 1 + sex + race,
    "adult" = freq ~ 1 + sex + race
  )
  
  var_exp <- var_exp_vec[3]
  diff_tbl <- purrr::map_df(var_exp_vec, function(var_exp) {
    print(var_exp)
    sel_vec <- data_tidy_mod[[var_exp_to_col[[var_exp]]]] %in%
      var_exp_to_lvl[[var_exp]]
    data_tidy_mod_diff <- data_tidy_mod[sel_vec,]
    if (var_exp == "adult") {
      data_tidy_mod_diff <- data_tidy_mod_diff %>%
        dplyr::mutate(age = factor(
          age, 
          levels = c("infant", "adult")
        )) 
      data_tidy_mod_diff <- data_tidy_mod_diff %>%
        dplyr::filter(grp %in% c("bcg", "day_365"))
      data_tidy_mod_diff <- data_tidy_mod_diff %>%
        dplyr::mutate(
          grp = as.character(grp),
          grp = purrr::map_chr(grp, function(x) {
            switch(
              x,
              "day_0" = "no bcg", 
              "day_365" = "bcg", 
              x
              )
          }) 
        )
    }
    grp_vec <- unique(data_tidy_mod_est_ci$grp) %>%
      as.character()
    grp <- grp_vec[1] 
    fit_large <- try(quantreg::rq(
      var_exp_to_fml_trt[[var_exp]], 
      tau = 0.5,
      data = data_tidy_mod_diff
    ), silent = TRUE)
    fit_small <- try(quantreg::rq(
      var_exp_to_fml_null[[var_exp]], 
      tau = 0.5,
      data = data_tidy_mod_diff
    ), silent = TRUE)
    anova_fit <- anova(fit_large, fit_small)
    p <- anova_fit$table$pvalue
    mod_summ <- summary(fit_large)
    coef_tbl <- coefficients(mod_summ) 
    ind_var_exp <- which(rownames(coef_tbl) == paste0(
      var_exp_to_col[[var_exp]], 
      var_exp
    ))
    coef_vec <- coef_tbl[ind_var_exp, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[ind_var_exp, "coefficients"]
    tibble::tibble(
      pop =  gsub("_\\w*", "", pop_pop_sub),
      age = age, 
      pop_pop_sub = pop_pop_sub, 
      pop_sub = gsub("\\w+_", "", pop_pop_sub), 
      var_exp = var_exp,
      diff_est = coef_est,
      diff_lb = coef_vec[1], 
      diff_ub = coef_vec[2], 
      diff_p = p
      ) %>%
      dplyr::mutate(
        pop =  gsub("\\+\\w*|\\-\\w*", "", pop)
      )
  })
  
  diff_tbl <- diff_tbl %>%
    dplyr::left_join(
      est_ci_tbl %>%
        dplyr::filter(!grp %in% c("no bcg", "day_0")) %>%
        dplyr::rename(var_exp = grp) %>%
        dplyr::select(var_exp, sd_std) %>%
        dplyr::bind_rows(
          est_ci_tbl %>%
            dplyr::filter(!grp %in% c("no bcg", "day_0")) %>%
            dplyr::rename(var_exp = grp) %>%
            dplyr::select(var_exp, sd_std) %>%
            dplyr::summarise(sd_std = mean(sd_std)) %>%
            dplyr::mutate(var_exp = "adult")
        )
    ) %>%
    dplyr::mutate(
      diff_est_std = diff_est / sd_std, 
      diff_lb_std = diff_lb / sd_std, 
      diff_ub_std = diff_ub / sd_std, 
    ) %>%
    dplyr::select(
      -c(diff_est, diff_lb, diff_ub)
    )
  list("est_ci_tbl" = est_ci_tbl, 
       "diff_tbl" = diff_tbl)
})

results_tbl_fig6_est_ci <- purrr::map_df(results_list_fig6, function(x) x$est_ci_tbl) %>%
  dplyr::mutate(pop = as.character(pop))
results_tbl_fig6_diff <- purrr::map_df(results_list_fig6, function(x) x$diff_tbl) %>%
  dplyr::group_by(
    var_exp
  ) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonferroni")) %>%
  dplyr::ungroup()
```

### Results

#### Effect of BCG in infants

```{r }
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "bcg") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p)
```

#### Effect of BCG in adult

```{r }
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "day_365") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p)
```

#### Effect of age amongst BCG-vaccinated participants

```{r }
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "adult") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p)
```

### Plots

```{r }
pop_to_lab_hladr <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (MFI)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (MFI)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM T cells (MFI)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste(" T cells (MFI)")))),                     
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (MFI)"))))
)

pop_to_lab_hladr_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

```{r , include = FALSE}
plot_list_fig6 <- get_fig_6_sub_plots()

plot_list_align <- purrr::map(seq_along(plot_list_fig6), function(i) {
  list(ggplot() + geom_blank() + theme_void(), 
       plot_list_fig6[[i]]$p_grp,
       ggplot() + geom_blank() + theme_void())
})

p_fig6_grp <- cowplot::plot_grid(
  plotlist = plot_list_align %>%
    purrr::flatten(), 
  ncol = 6,
  rel_widths = c(0.15, 2, 1, 0.15, 2, 1), 
  align = "hv", 
  axis = "lrtb"
)

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_6-grp.pdf"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig6_grp, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
od(path_fig_rel_pdf)

p_fig6_diff <- p_fig6_grp
nudge_y_diff <- 0
y_vec <- rep(1 - 1/3 * 1:3, each = 2) + nudge_y_diff

for(i in seq_along(plot_list_fig6)) {
  p_fig6_diff <- p_fig6_diff +
    cowplot::draw_plot(
      plot_list_fig6[[i]]$p_diff, 
      width = 1/6, 
      height = 1/3 - nudge_y_diff - 0.0105, 
      x = x_vec[i], 
      y = y_vec[i]
    ) 
}

x_vec_hladr <- rep(c(0.02, 0.52), 3)
y_vec_hladr <- rep(0.5, 6)
nudge_down <- 0.0125
p_fig6_diff <- p_fig6_diff + 
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.03, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.54, 
      y = 0.885 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.0175, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
      text = "HLADR+", 
      x = 0.5275, 
      y = 0.5525 - nudge_down, 
      angle = 90, 
      hjust = 0.5, 
      vjust = 0.5
    ) +
  cowplot::draw_text(
    text = "HLADR+", 
    x = 0.036375, 
    y = 0.2167 - nudge_down, 
    angle = 90, 
    hjust = 0.5, 
    vjust = 0.5
  ) 

plot_tbl_legend <- tibble::tibble(
  x = c(0.5, 0.5), 
  y = c(0.6, 0.5), 
  col = c("red", "dodgerblue"), 
  shape = c("circle"), 
  lbl = c("Pre-BCG", "Post-BCG")
)

p_legend <- ggplot(plot_tbl_legend) + 
  theme_void() + 
  geom_point(aes(x, y, col = col), 
             show.legend = FALSE, 
             size = 2, alpha = 0.5) +
  lims(x = 0:1, y = 0:1) +
  geom_text(aes(x = x + 0.05, y, label = lbl), 
            hjust = 0, size = 4.25) +
  scale_colour_manual(
    values = c(
      "red" = "red", 
      "dodgerblue" = "dodgerblue"
    )
  )
p_fig6 <- p_fig6_diff + 
  cowplot::draw_plot(
    plot = p_legend, 
    y = 0, 
    x = 1/2, 
    width = 1/2, 
    height = 1/4
  )
  

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_6.pdf"
  )
path_fig_rel_png <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_6.png"
  )
cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_fig6, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
od(path_fig_rel_pdf)
cowplot::ggsave2(
  path_fig_rel_png, 
  p_fig6, 
  height = 29 * 3/4, 
  width = 19, 
  units = "cm"
)
```
