# Figure 6

## Relevant criticisms

## Proposed approach

## Data exploration

```{r }
data_raw_fig6 <- DataTidyGelaDURT::data_tidy_mem %>%
    dplyr::mutate(
      grp = ifelse(age == "adult", paste0("day_", grp), grp)
    ) %>%
    dplyr::filter(
      grp %in% c("no bcg", "bcg", "day_0", "day_365")
    )
  
pop_vec <- c("mait", "nkt", "gd", "cd4")
pop_sub_vec <- c(
  "CD45RA+CCR7+", "CD45RA-CCR7+", "CD45RA-CCR7-", "CD45RA+CCR7-" 
)
data_raw_fig6 <- data_raw_fig6 %>%
  dplyr::mutate(
    pop = factor(
      pop, 
      levels = pop_vec
    ), 
    pop_sub = factor(
      pop_sub, 
      levels = pop_sub_vec
    )
  ) %>%
  dplyr::mutate(
    grp = factor(
      grp, 
      levels = c(
        "no bcg", 
        "bcg", 
        "day_0", 
        "day_365"
      )
    )
  )
data_tidy_clin <- data_tidy_clin_adult %>%
  dplyr::select(pid, race, sex) %>%
  dplyr::bind_rows(
    data_tidy_clin_infant %>%
      dplyr::select(pid, race, sex) %>%
      dplyr::mutate(race = ifelse(race == "coloured", "non_black", race))
  )

data_tidy_fig6 <- data_raw_fig6 %>%
  dplyr::left_join(
    data_tidy_clin, 
    by = "pid"
  ) %>%
  dplyr::mutate(
    race = factor(race, 
              levels = c("non_black", "black")), 
    sex = factor(
      sex, 
      levels = c("female", "male")
    )
  )

data_tidy_fig6 <- data_tidy_fig6 %>%
  dplyr::mutate(
    x_order = paste0(pop_sub, "_", grp)
  ) %>%
  dplyr::arrange(
    pop, pop_sub, grp
  )

chr_to_num_x_order <- setNames(
  seq_along(unique(data_tidy_fig6$x_order)), 
  unique(data_tidy_fig6$x_order)
)
data_tidy_fig6 <- data_tidy_fig6 %>%
  dplyr::mutate(
    x_order_num = chr_to_num_x_order[x_order]
  ) %>%
  dplyr::mutate(
    pop_x_order = paste0(pop, "_", x_order), 
    pop_pop_sub = paste0(pop, "_", pop_sub)
  )
x_order_vec <- unique(data_tidy_fig6$x_order)
pop_x_order_vec <- unique(data_tidy_fig6$pop_x_order)
pop_pop_sub_vec <- unique(data_tidy_fig6$pop_pop_sub)

pop_sub_grp_to_x_order_inc_num <- data_tidy_fig6 %>%
  dplyr::group_by(pop_sub, grp, x_order) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::select(pop_sub, grp, x_order, x_order_num) %>%
  dplyr::mutate(x_order = factor(
    x_order, 
    levels = x_order
  ))
```

```{r }
pop_to_lab_mem <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (%)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (%)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM+ T cells (%)")))),
  "gem" = bquote(paste(plain(paste("GEM T cells (%)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste("TCR+ cells (%)")))), 
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (%)")))), 
  "cd4_ifng" = bquote(paste(plain(paste("IFN")), gamma, plain(paste("+CD4+ T cells (%)"))))
)

pop_to_lab_mem_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

### Identity transformation

```{r }
p <- ggplot(
  data_tidy_fig6 %>%
    dplyr::mutate(
      grp = factor(
        grp, 
        levels = c("no bcg", "bcg", "day_0", "day_365")
      )
    ), 
  aes(x = x_order, fill = pop_sub)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "xy") +
  geom_boxplot(aes(y = freq)) +
  facet_wrap(~pop, ncol = 4) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  scale_x_discrete(
    breaks = x_order_vec, 
    limits = x_order_vec
  )
for (x in unique(data_tidy_fig6$x_order)) {
  p <- p + 
    ggforce::geom_sina(aes(y = freq, shape = grp), maxwidth = 0.75, 
                       scale = "width", 
                       data = data_tidy_fig6 %>%
                         dplyr::filter(x_order == x))
}
p 
```

### Square root transformation

```{r }
p +
  scale_y_sqrt()
```

It generally seems that the square root transformation makes the data nicer to work with, as long as the median response is less than 0.75. Above that the identity transformation using the beta distribution may work better, especially for those capped at 100. In that case, the frequencies should be divided by 100 to work with proportions instead. 

## Analysis

### Calculation

```{r , include = FALSE}
pop_pop_sub_to_trans_obj_tbl <- data_tidy_fig6 %>%
  dplyr::group_by(pop_pop_sub, grp) %>%
  dplyr::summarise(med = median(freq, na.rm = TRUE),
                   .groups = "drop_last"
                   ) %>%
  dplyr::summarise(trans = list(switch(
    as.character(any(med > 0.5)), 
    "TRUE" = scales::identity_trans(), 
    "FALSE" = scales::sqrt_trans()
  )))
pop_pop_sub_to_trans_obj <- pop_pop_sub_to_trans_obj_tbl$trans %>%
  setNames(pop_pop_sub_to_trans_obj_tbl$pop_pop_sub)
```

```{r , include = FALSE}
pop_pop_sub <- pop_pop_sub_vec[1]
results_list_fig6 <- purrr::map(pop_pop_sub_vec, function(pop_pop_sub) {
  data_tidy_mod <- data_tidy_fig6 %>%
    dplyr::filter(pop_pop_sub == .env$pop_pop_sub) 
  
  trans_obj <- pop_pop_sub_to_trans_obj[[pop_pop_sub]]
  
  data_tidy_mod <- data_tidy_mod %>%
    dplyr::mutate(prop = freq / 1e2) %>%
    dplyr::mutate(prop = trans_obj$transform(prop))
  
  # =======================
  # get estimates and ci
  # =======================
  
  age_vec <- unique(data_tidy_mod$age)
  age <- age_vec[1]
  est_ci_tbl <- purrr::map_df(age_vec, function(age) {
    data_tidy_mod_est_ci  <- data_tidy_mod %>%
      dplyr::filter(age == .env$age)
    grp_vec <- unique(data_tidy_mod_est_ci$grp) %>%
      as.character()
    grp <- grp_vec[1] 
    purrr::map_df(grp_vec, function(grp) {
      print(grp)
      data_tidy_mod_est_ci_grp <- data_tidy_mod_est_ci %>%
        dplyr::mutate(
          grp = factor(
            grp, 
            levels = c(
              .env$grp, 
              setdiff(grp_vec, .env$grp)
            )
          )
        )
      # calculate residual standard deviation
      fit_large <- try(quantreg::rq(
        freq ~ 1 + grp + sex + race, 
        tau = 0.5,
        data = data_tidy_mod_est_ci_grp
      ), silent = TRUE)
      
      sd_std = sd(resid(summary(fit_large, se = "rank")))
      
      # calculate unadjusted eff and ci
      fit_large <- try(quantreg::rq(
        freq ~ 1 + grp, 
        tau = 0.5,
        data = data_tidy_mod_est_ci_grp
      ), silent = TRUE)
      mod_summ <- summary(fit_large, se = "rank")

      coef_tbl <- coefficients(mod_summ)
      coef_vec <- coef_tbl[1, c("lower bd", "upper bd")] %>%
        as.vector()
      coef_est <- coef_tbl[1, "coefficients"]
      
      sd_std = sd(resid(summary(fit_large, se = "rank")))
      tibble::tibble(
        pop = data_tidy_mod_est_ci_grp$pop[[1]],
        age = age, 
        pop_sub = gsub("\\w+_", "", pop_pop_sub), 
        grp = grp, 
        sd_std = sd_std,
        est = coef_est,
        lb = coef_vec[1], 
        ub = coef_vec[2]
        ) %>%
        dplyr::mutate(
          est = trans_obj$inverse(est), 
          lb = trans_obj$inverse(lb), 
          ub = trans_obj$inverse(ub)
        )
    })
  })
  
  # =======================
  # get diff est, ci and p-value
  # =======================
  
  var_exp_vec <- c("bcg", "day_365", "adult_bcg", "adult_no_bcg")
  var_exp_to_lvl <- list(
    "bcg" = c("no bcg", "bcg"), 
    "day_365" = c("day_0", "day_365"), 
    "adult_bcg" = c("infant", "adult"),
    "adult_no_bcg" = c("infant", "adult")
  )
  var_exp_to_col <- c(
    "bcg" = "grp", 
    "day_365" = "grp", 
    "adult_bcg" = "age",
    "adult_no_bcg" = "age"
  )
  var_exp <- var_exp_vec[1]
  var_exp_to_fml_trt <- list(
    "bcg" = freq ~ 1 + grp + sex + race, 
    "day_365" = freq ~ 1 + grp + sex + race,
    "adult_bcg" = freq ~ 1 + age + sex + race,
    "adult_no_bcg" = freq ~ 1 + age + sex + race
  )
  var_exp_to_fml_null <- list(
    "bcg" = freq ~ 1  + sex + race, 
    "day_365" = freq ~ 1 + sex + race,
    "adult_bcg" = freq ~ 1 + sex + race,
    "adult_no_bcg" = freq ~ 1 + sex + race
  )
  
  var_exp <- var_exp_vec[3]
  diff_tbl <- purrr::map_df(var_exp_vec, function(var_exp) {
    print(var_exp)
    sel_vec <- data_tidy_mod[[var_exp_to_col[[var_exp]]]] %in%
      var_exp_to_lvl[[var_exp]]
    data_tidy_mod_diff <- data_tidy_mod[sel_vec,]
    if (grepl("adult", var_exp)) {
      data_tidy_mod_diff <- data_tidy_mod_diff %>%
        dplyr::mutate(age = factor(
          age, 
          levels = c("infant", "adult")
        )) 
      bcg_lvl <- ifelse(var_exp == "adult_bcg", "bcg", "")
      bcg_lvl <- ifelse(var_exp == "adult_no_bcg", "no bcg", bcg_lvl)
      data_tidy_mod_diff <- data_tidy_mod_diff %>%
        dplyr::filter(grp %in% c(bcg_lvl, "day_365"))
    }
    grp_vec <- unique(data_tidy_mod$grp) %>%
      as.character()
    grp <- grp_vec[1] 
    fit_large <- try(quantreg::rq(
      var_exp_to_fml_trt[[var_exp]], 
      tau = 0.5,
      data = data_tidy_mod_diff
    ), silent = TRUE)
    fit_small <- try(quantreg::rq(
      var_exp_to_fml_null[[var_exp]], 
      tau = 0.5,
      data = data_tidy_mod_diff
    ), silent = TRUE)
    anova_fit <- anova(fit_large, fit_small)
    p <- anova_fit$table$pvalue
    mod_summ <- summary(fit_large)
    coef_tbl <- coefficients(mod_summ) 
    ind_var_exp <- which(rownames(coef_tbl) == paste0(
      var_exp_to_col[[var_exp]], 
      switch(
        var_exp,
        "adult_no_bcg" = ,
        "adult_bcg" = "adult", 
        var_exp
      )
    ))
    coef_vec <- coef_tbl[ind_var_exp, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[ind_var_exp, "coefficients"]
    tibble::tibble(
      pop =  gsub("_\\w*", "", pop_pop_sub),
      age = age, 
      pop_sub = gsub("\\w+_", "", pop_pop_sub), 
      var_exp = var_exp,
      diff_est = coef_est,
      diff_lb = coef_vec[1], 
      diff_ub = coef_vec[2], 
      diff_p = p
      ) %>%
      dplyr::mutate(
        pop =  gsub("\\+\\w*|\\-\\w*", "", pop)
      )
  })
  
  diff_tbl <- diff_tbl %>%
    dplyr::left_join(
      est_ci_tbl %>%
        dplyr::filter(!grp %in% c("no bcg", "day_0")) %>%
        dplyr::rename(var_exp = grp) %>%
        dplyr::select(var_exp, sd_std) %>%
        dplyr::bind_rows(
          purrr::map_df(c("adult_bcg", "adult_no_bcg"), function(x) {
            est_ci_tbl %>%
              dplyr::filter(!grp %in% c("no bcg", "day_0")) %>%
              dplyr::rename(var_exp = grp) %>%
              dplyr::select(var_exp, sd_std) %>%
              dplyr::summarise(sd_std = mean(sd_std)) %>%
              dplyr::mutate(var_exp = x)
          })
        ) 
    ) %>%
    dplyr::mutate(
      diff_est_std = diff_est / sd_std, 
      diff_lb_std = diff_lb / sd_std, 
      diff_ub_std = diff_ub / sd_std, 
    ) %>%
    dplyr::select(
      -c(diff_est, diff_lb, diff_ub)
    )
  list("est_ci_tbl" = est_ci_tbl, 
       "diff_tbl" = diff_tbl)
})

results_tbl_fig6_est_ci <- purrr::map_df(results_list_fig6, function(x) x$est_ci_tbl) %>%
  dplyr::mutate(pop = as.character(pop)) %>%
  dplyr::select(-sd_std)
results_tbl_fig6_diff <- purrr::map_df(results_list_fig6, function(x) x$diff_tbl) %>%
  dplyr::mutate(var_exp_orig = var_exp) %>%
  dplyr::mutate(
    var_exp = purrr::map_chr(var_exp, function(x) {
      switch(
        x,
        "adult_no_bcg" = ,
        "adult_bcg" = "adult", 
        x
        )
    }) 
  ) %>%
  dplyr::group_by(
    var_exp_orig
  ) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonferroni")) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    var_exp = var_exp_orig
  ) %>%
  dplyr::select(-var_exp_orig)
```

### Results

#### Effect of BCG in infants

Moderate effects with highly-significant p-values for $\gamma\delta$ T cells, where `CD45RA-CCR7-` seem to become
`CD45RA+CCR7+` cells. Increase in `CD45RA+CCR7-` $\gamma\delta$ T cells, with `p=0.019` but `q = 0.3`. 

Some support for an increase in `CD45RA-CCR7+` MAIT cells (p = 0.009; q = 0.14). 

```{r , results = "asis"}
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "bcg") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p) %>%
  pander::pandoc.table()
```

#### Effect of BCG in adults

No clear effect.

```{r , results = "asis"}
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "day_365") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p) %>%
  pander::pandoc.table()
```

#### Effect of age amongst BCG-(re)vaccinated participants

Strong effects on CD4 T cells, as expected. 

Strong effects also for MAIT cells, with `CD45RA+CCR7-` becoming  `CD45RA-CCR7-`.

Small but significant decrease in `CD45RA+CCR7-` NKT cells (q = 0.005). Seem to become either `CD45RA-CCR7-` (p = 0.08; q = 1) or `CD45RA+CCR7+` (p = 0.13; q = 1) cells. 

```{r , results = "asis"}
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "adult_bcg") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p) %>%
  pander::pandoc.table()
```

#### Effect of age amongst non-BCG-(re)vaccinated participants

Observed the same effects for CD4 T and MAIT cells as in the BCG-vaccinated groups. 

Smaller and non-significant decrease in `CD45RA+CCR7-` NKT cells (p = 0.06; q = 0.96).

Non-significant (after multiple comparisons) reduction in `CD45RA-CCR7-` $\gamma\delta$ T cells (p = 0.0465; q = 0.74) that was non-significant but in the same direction in BCG-vaccinated infants (p = 0.045; q = 1).

```{r , results = "asis"}
results_tbl_fig6_diff %>%
  dplyr::filter(var_exp == "adult_no_bcg") %>%
  dplyr::select(pop, pop_sub, diff_est_std, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p) %>%
  pander::pandoc.table()
```

### Plots

```{r }
pop_to_lab_mem <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (%)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (%)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM T cells (%)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste(" T cells (%)")))),                     
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (%)"))))
)

pop_to_lab_mem_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

```{r }
plot_list_fig6 <- get_fig_6_sub_plots()
p_grp_width <- 0.75
nudge_x_diff <- -0.0167
nudge_width_marker <- - 0.05
prop_upper_plot <- 0.85
stretch_height_lower_plot <- 1.67
p_out <- cowplot::ggdraw()
for(i in 1:4) {
  y_base <- 1 - 0.25 * i
  p_out <- p_out + 
    cowplot::draw_plot(
      plot = plot_list_fig6[[i]]$p_grp, 
      width = p_grp_width, 
      height = 1/4 * prop_upper_plot, 
      y = 1/4 * (1 - prop_upper_plot) + y_base
    ) +
    cowplot::draw_plot(
      plot = plot_list_fig6[[i]]$p_diff, 
      width = 1 - p_grp_width - nudge_x_diff,
      x = p_grp_width + nudge_x_diff,
      height = 1/4 * prop_upper_plot, 
      y = 1/4 * (1 - prop_upper_plot) + y_base
    )  +
    cowplot::draw_plot(
      plot = plot_list_fig6[[i]]$p_marker, 
      y = y_base, 
      height = (1/4 * (1 - prop_upper_plot)) * stretch_height_lower_plot, 
      width = p_grp_width, 
      x = 0
    ) +
    cowplot::draw_plot(
      plot = plot_list_fig6[[i]]$p_marker +
        theme(axis.text.y = element_blank()) +
        theme(axis.ticks.y = element_blank()), 
      y =  y_base, 
      height = (1/4 * (1 - prop_upper_plot)) * stretch_height_lower_plot, 
      width = 1 - p_grp_width + nudge_width_marker, 
      x = p_grp_width - nudge_width_marker
    )
}
path_fig_grp <- file.path(dir_fig_manu, "fig_6-grp.pdf")

label_tbl <- tibble::tibble(
  lbl = LETTERS[1:4],
  x = 0.025, 
  y = seq(1, 0.25, by = -0.25) - 0.01
)
for(i in seq_len(nrow(label_tbl))) {
  p_out <- p_out + 
    cowplot::draw_text(
      text = label_tbl$lbl[i],
      x = label_tbl$x[i],
      y = label_tbl$y[i]
    )
}

# Plot legend
# =====================


grp_to_col = trt_to_col[c(
  "no bcg",
  "bcg",
  "day_0",
  "day_365"
)]
grp_to_x <- setNames(
  rep(c(0, 0.25), each = 2) + 0.125, # was 0.225
  names(grp_to_col)
)

grp_to_y <- setNames(
  rep(c(0.5, 0.3), 2),
  names(grp_to_col)
)
grp_to_lab <- setNames(
  c("Infant: no BCG",
    "Infant: BCG", 
    "Adult: before BCG", 
    "Adult: after BCG"),
  names(grp_to_y)
)
plot_tbl_legend_grp <- purrr::map_df(unique(names(grp_to_col)), function(grp) {
  tibble::tibble(
    grp = grp, 
    x = grp_to_x[grp], 
    y = grp_to_y[grp],
    lbl = grp_to_lab[grp]
  )
})

var_exp_to_y <- setNames(
  rev(c(0.2, 0.4, 0.6)) - 0.1, 
  names(var_exp_to_fill)
)
var_exp_to_x <- setNames(
  rep(0.725, 3), 
  names(var_exp_to_fill)
)
var_exp_to_lab <- setNames(
  c("BCG: infant",
    "BCG: adult", 
    "Adult vs infant: BCG vacc."),
  names(var_exp_to_fill)
)
plot_tbl_legend_diff <- purrr::map_df(rev(unique(names(var_exp_to_x))), function(var_exp) {
  tibble::tibble(
    var_exp = var_exp, 
    x = var_exp_to_x[var_exp], 
    y = var_exp_to_y[var_exp],
    lbl = var_exp_to_lab[var_exp]
  )
})
p_legend <- ggplot() + 
  theme_void() + 
  geom_point(
    data = plot_tbl_legend_grp, 
    aes(x = x - 0.0175, y = y, col = grp), 
    size = 3, alpha = 0.65
  ) +
  geom_text(
    data = tibble::tibble(
      x = 0.42, 
      y = 0.9, 
      lbl = "Phenotype, age and BCG status"
    ), 
    aes(x = x, y = y, label = lbl), 
    hjust = 0.5, 
    vjust = 0, 
    size = 4.21 
  ) +
  geom_text(
    data = tibble::tibble(
      x = 0.94375, 
      y = 0.7, 
      lbl = "Phenotype and\neffect type"
    ), 
    aes(x = x, y = y, label = lbl), 
    hjust = 0.5, 
    vjust = 0, 
    size = 4.21 
  ) +
  geom_text(
    data = plot_tbl_legend_grp, 
    aes(x = x, y = y - 0.05, label = lbl), 
    hjust = 0, 
    vjust = 0, 
    size = 4.25 
  ) +
  geom_point(
    data = plot_tbl_legend_diff %>%
      dplyr::mutate(grp = var_exp), 
    aes(x = x + 0.0075, y = y, fill = var_exp, 
        shape = grp), 
    size = 3
  ) +
  geom_text(
    data = plot_tbl_legend_diff, 
    aes(x = x + 0.025, y = y - 0.05, label = lbl), 
    hjust = 0, 
    vjust = 0, 
    size = 4.25 
  ) +
  scale_colour_manual(
    values = trt_to_col
  ) +
  scale_shape_manual(
    values = var_exp_to_shape
  ) +
  scale_fill_manual(
    values = var_exp_to_fill 
  ) +
  lims(x = c(0,1), y = c(0,1)) +
  guides("alpha" = "none", "colour" = "none", 
         "fill" = "none", 
         "shape" = "none") 

plot_frac <- 0.89
plot_legend_add_height <- 0
p_test_full <- cowplot::ggdraw() + 
  cowplot::draw_plot(
    plot = p_out, 
    height = plot_frac, 
    y = 1 - plot_frac
  ) +
  cowplot::draw_plot(
    plot = p_legend, 
    y = 0, 
    x = 0, 
    width = 1, 
    height = 1 - plot_frac + plot_legend_add_height
  )

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_6.pdf"
  )
path_fig_rel_png <- file.path(
    dir_fig_vec_rel["manu"],
    "fig_6.png"
  )

cowplot::ggsave2(
  path_fig_rel_png, 
  p_test_full, 
  height = 29.4, 
  width = 19, 
  units = "cm",
  dpi = 300 * (1 + params$high_res * 4)
)

cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_test_full, 
  height = 29.4, 
  width = 19, 
  units = "cm",
  dpi = 300 * (1 + params$high_res * 4)
)
```

```{r , results = "asis"}
knitr::include_graphics(path_fig_rel_png)
```

