# Supplementary Figure 2

## Relevant criticisms

- 3.8
  - No formal statistical analysis done

## Proposed approach

- Similar to figure 6 graphically, but tests the same as figure 4

## Proposed approach

## Data exploration

```{r }
data_raw_fig2s <- DataTidyGelaDURT::data_tidy_mem %>%
  dplyr::filter(age == "adult") %>%
  dplyr::mutate(
    grp = ifelse(age == "adult", paste0("day_", grp), grp)
  ) 
  
pop_vec <- c("mait", "nkt", "gd", "cd4")
pop_sub_vec <- c(
  "CD45RA+CCR7+", "CD45RA-CCR7+", "CD45RA-CCR7-", "CD45RA+CCR7-" 
)
data_raw_fig2s <- data_raw_fig2s %>%
  dplyr::mutate(
    pop = factor(
      pop, 
      levels = pop_vec
    ), 
    pop_sub = factor(
      pop_sub, 
      levels = pop_sub_vec
    )
  ) %>%
  dplyr::mutate(
    grp = factor(
      grp, 
      levels = c(
        "day_0", 
        "day_21",
        "day_35", 
        "day_365"
      )
    )
  )

data_tidy_clin <- data_tidy_clin_adult %>%
  dplyr::select(pid, race, sex)

data_tidy_fig2s <- data_raw_fig2s %>%
  dplyr::left_join(
    data_tidy_clin, 
    by = "pid"
  ) %>%
  dplyr::mutate(
    race = factor(race, 
              levels = c("non_black", "black")), 
    sex = factor(
      sex, 
      levels = c("female", "male")
    )
  )

data_tidy_fig2s <- data_tidy_fig2s %>%
  dplyr::mutate(
    x_order = paste0(pop_sub, "_", grp)
  ) %>%
  dplyr::arrange(
    pop, pop_sub, grp
  )

chr_to_num_x_order <- setNames(
  seq_along(unique(data_tidy_fig2s$x_order)), 
  unique(data_tidy_fig2s$x_order)
)
data_tidy_fig2s <- data_tidy_fig2s %>%
  dplyr::mutate(
    x_order_num = chr_to_num_x_order[x_order]
  ) %>%
  dplyr::mutate(
    pop_x_order = paste0(pop, "_", x_order), 
    pop_pop_sub = paste0(pop, "_", pop_sub)
  )
x_order_vec <- unique(data_tidy_fig2s$x_order)
pop_x_order_vec <- unique(data_tidy_fig2s$pop_x_order)
pop_pop_sub_vec <- unique(data_tidy_fig2s$pop_pop_sub)

pop_sub_grp_to_x_order_inc_num <- data_tidy_fig2s %>%
  dplyr::group_by(pop_sub, grp, x_order) %>%
  dplyr::slice(1) %>%
  dplyr::ungroup() %>%
  dplyr::select(pop_sub, grp, x_order, x_order_num) %>%
  dplyr::mutate(x_order = factor(
    x_order, 
    levels = x_order
  ))
```

```{r }
pop_to_lab_mem <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (%)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (%)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM+ T cells (%)")))),
  "gem" = bquote(paste(plain(paste("GEM T cells (%)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste("TCR+ cells (%)")))), 
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (%)")))), 
  "cd4_ifng" = bquote(paste(plain(paste("IFN")), gamma, plain(paste("+CD4+ T cells (%)"))))
)

pop_to_lab_mem_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

### Identity transformation

```{r }
p <- ggplot(
  data_tidy_fig2s %>%
    dplyr::mutate(
      grp = factor(
        grp, 
        levels = c("no bcg", "bcg", "day_0", "day_365")
      )
    ), 
  aes(x = x_order, fill = pop_sub)
) +
  cowplot::theme_cowplot() +
  cowplot::background_grid(major = "xy") +
  geom_boxplot(aes(y = freq)) +
  facet_wrap(~pop, ncol = 4) +
  theme(axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) +
  scale_x_discrete(
    breaks = x_order_vec, 
    limits = x_order_vec
  )
for (x in unique(data_tidy_fig2s$x_order)) {
  p <- p + 
    ggforce::geom_sina(aes(y = freq, shape = grp), maxwidth = 0.75, 
                       scale = "width", 
                       data = data_tidy_fig2s %>%
                         dplyr::filter(x_order == x))
}
p 
```

### Square root transformation

```{r }
p +
  scale_y_sqrt()
```

It generally seems that the square root transformation makes the data nicer to work with, as long as the median response is less than 0.75. Above that the identity transformation using the beta distribution may work better, especially for those capped at 100. In that case, the frequencies should be divided by 100 to work with proportions instead. 

## Analysis

### Calculation

```{r }
pop_pop_sub_to_trans_obj_tbl <- data_tidy_fig2s %>%
  dplyr::group_by(pop_pop_sub, grp) %>%
  dplyr::summarise(med = median(freq, na.rm = TRUE),
                   .groups = "drop_last"
                   ) %>%
  dplyr::summarise(trans = list(switch(
    as.character(any(med > 0.5)), 
    "TRUE" = scales::identity_trans(), 
    "FALSE" = scales::sqrt_trans()
  )))
pop_pop_sub_to_trans_obj <- pop_pop_sub_to_trans_obj_tbl$trans %>%
  setNames(pop_pop_sub_to_trans_obj_tbl$pop_pop_sub)
```

```{r }
pop_pop_sub <- pop_pop_sub_vec[1]
results_list_fig2s <- purrr::map(pop_pop_sub_vec, function(pop_pop_sub) {
  data_tidy_mod <- data_tidy_fig2s %>%
    dplyr::filter(pop_pop_sub == .env$pop_pop_sub) 
  
  trans_obj <- pop_pop_sub_to_trans_obj[[pop_pop_sub]]
  
  data_tidy_mod_est_ci <- data_tidy_mod %>%
    dplyr::mutate(prop = freq / 1e2) %>%
    dplyr::mutate(prop = trans_obj$transform(prop))
  
  # =======================
  # get estimates and ci
  # =======================

  grp_vec <- unique(data_tidy_mod$grp) %>%
    as.character()
  grp <- grp_vec[1] 
  est_ci_tbl <- purrr::map_df(grp_vec, function(grp) {
    print(grp)
    data_tidy_mod_est_ci_grp <- data_tidy_mod_est_ci %>%
      dplyr::mutate(
        grp = factor(
          grp, 
          levels = c(
            .env$grp, 
            setdiff(grp_vec, .env$grp)
          )
        )
      )
    
    # calculate unadjusted eff and ci
    fit_large <- try(quantreg::rq(
      freq ~ 1 + grp, 
      tau = 0.5,
      data = data_tidy_mod_est_ci_grp
    ), silent = TRUE)
    mod_summ <- summary(fit_large, se = "rank")

    coef_tbl <- coefficients(mod_summ)
    coef_vec <- coef_tbl[1, c("lower bd", "upper bd")] %>%
      as.vector()
    coef_est <- coef_tbl[1, "coefficients"]
    
    tibble::tibble(
      pop = data_tidy_mod_est_ci_grp$pop[[1]],
      pop_sub = gsub("\\w+_", "", pop_pop_sub), 
      grp = grp, 
      est = coef_est,
      lb = coef_vec[1], 
      ub = coef_vec[2]
      ) %>%
      dplyr::mutate(
        est = trans_obj$inverse(est), 
        lb = trans_obj$inverse(lb), 
        ub = trans_obj$inverse(ub)
      )
    })
  
  # =======================
  # get diff est, ci and p-value
  # =======================
  
  shift_within_01 <- function(x) {
      range_x <- range(x)
      diff_x <- diff(range_x)
      # now (not strictly) within 0,1
      x <- (x - range_x[1])/diff_x
      # strictly within 01:
      small_diff <- diff_x * 0.005
      pmax(small_diff, pmin(x, range_x[2] - small_diff))
  }
  
  data_tidy_mod_diff <- data_tidy_mod %>%
    dplyr::filter(!is.na(freq)) %>%
    dplyr::mutate(prop = freq / 1e2) %>%
    dplyr::mutate(prop = shift_within_01(prop))
  
  # overall p-value
  fit_large_overall <- glmmTMB::glmmTMB(
     prop ~ 1 + grp + sex + race + (1|pid), 
    data = data_tidy_mod_diff, 
    family = glmmTMB::beta_family()
  )
  fit_small_overall <- glmmTMB::glmmTMB(
    prop ~ 1 + sex + race + (1|pid), 
    data = data_tidy_mod_diff, 
    family = glmmTMB::beta_family()
  )
  diff_p_overall_mm <- modutils:::.test_lr(
    mod_large = fit_large_overall, 
    mod_small = fit_small_overall
  )$p
  
  diff_tbl <- tibble::tibble(
    pop =  gsub("_\\w*", "", pop_pop_sub),
    pop_sub = gsub("\\w+_", "", pop_pop_sub), 
    diff_p = diff_p_overall_mm
    ) %>%
    dplyr::mutate(
      pop =  gsub("\\+\\w*|\\-\\w*", "", pop)
    )
  
  list("est_ci_tbl" = est_ci_tbl, 
       "diff_tbl" = diff_tbl)
})

results_tbl_fig2s_est_ci <- purrr::map_df(results_list_fig2s, function(x) x$est_ci_tbl) %>%
  dplyr::mutate(pop = as.character(pop))
results_tbl_fig2s_diff <- purrr::map_df(results_list_fig2s, function(x) x$diff_tbl) %>%
  dplyr::mutate(diff_p_bonf = p.adjust(diff_p, method = "bonferroni")) 
```

### Results

#### Effect of BCG in infants

Clear effect for TCRgd T cells. 

```{r }
results_tbl_fig2s_diff %>%
  dplyr::select(pop, pop_sub, diff_p, diff_p_bonf) %>%
  dplyr::arrange(diff_p)
```

### Plots

```{r }
pop_to_lab_mem <- c(
  "mait" = bquote(paste(plain(paste("MAIT cells (%)")))), 
  "nkt" = bquote(paste(plain(paste("NKT cells (%)")))),
  "cd1b" = bquote(paste(plain(paste("CD1b-GMM T cells (%)")))),
  "gd" = bquote(paste(gamma, delta, plain(paste(" T cells (%)")))),                     
  "cd4" = bquote(paste(plain(paste("CD4+ T cells (%)"))))
)

pop_to_lab_mem_diff <- c(
  "mait" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "nkt" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "cd1b" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gem" = bquote(paste(plain(paste("Standardised ")), Delta)),
  "gd" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4" = bquote(paste(plain(paste("Standardised ")), Delta)), 
  "cd4_ifng" = bquote(paste(plain(paste("Standardised ")), Delta))
)
```

```{r }
plot_list_fig2s <- get_fig_2s_sub_plots()
p_grp_width <- 1
nudge_width_marker <- - 0.05
prop_upper_plot <- 0.85
stretch_height_lower_plot <- 1.67
p_out <- cowplot::ggdraw()
for(i in 1:4) {
  y_base <- 1 - 0.25 * i
  p_out <- p_out + 
    cowplot::draw_plot(
      plot = plot_list_fig2s[[i]]$p_grp, 
      width = p_grp_width, 
      height = 1/4 * prop_upper_plot, 
      y = 1/4 * (1 - prop_upper_plot) + y_base
    ) +
    cowplot::draw_plot(
      plot = plot_list_fig2s[[i]]$p_diff, 
      width = 1 - p_grp_width,
      x = p_grp_width,
      height = 1/4 * prop_upper_plot, 
      y = 1/4 * (1 - prop_upper_plot) + y_base
    )  +
    cowplot::draw_plot(
      plot = plot_list_fig2s[[i]]$p_marker, 
      y = y_base, 
      height = (1/4 * (1 - prop_upper_plot)) * stretch_height_lower_plot, 
      width = p_grp_width, 
      x = 0
    ) 
}
path_fig_grp <- file.path(dir_fig_manu, "fig_2s-grp.pdf")

# Plot legend
# =====================

trt_vec_s2 <- paste0("day_", c(0, 21, 35, 365))

grp_to_x <- setNames(
  0.31 + seq(0, 0.4, length.out = 4),
  trt_vec_s2
)
grp_to_y <- setNames(
  rep(0.25, 4),
  trt_vec_s2
)
grp_to_lab <- setNames(
  c("Day 0",
    "Day 21", 
    "Day 35", 
    "Day 365"),
  trt_vec_s2
)
plot_tbl_legend_grp <- purrr::map_df(paste0("day_", c(0, 21, 35, 365)),
                                     function(grp) {
  tibble::tibble(
    grp = grp, 
    x = grp_to_x[grp], 
    y = grp_to_y[grp], 
    lbl = grp_to_lab[grp]
  )
})
p_legend <- ggplot() + 
  theme_void() + 
  geom_point(
    data = plot_tbl_legend_grp, 
    aes(x = x - 0.0175, y = y, col = grp), 
    size = 3, 
    alpha = 0.65
  ) +
  geom_text(
    data = tibble::tibble(
      x = 0.55, 
      y = 0.7, 
      lbl = "Phenotype and days since BCG re-vaccination"
    ), 
    aes(x = x, y = y, label = lbl), 
    hjust = 0.5, 
    vjust = 0, 
    size = 4.21 
  ) +
  geom_text(
    data = plot_tbl_legend_grp, 
    aes(x = x, y = y, label = lbl), 
    hjust = 0, 
    vjust = 0.5, 
    size = 4.25 
  ) +
  scale_colour_manual(
    values = trt_to_col
  ) +
  lims(x = c(0,1), y = c(0,1)) +
  guides("alpha" = "none", "colour" = "none", 
         "fill" = "none", 
         "shape" = "none") 

label_tbl <- tibble::tibble(
  lbl = LETTERS[1:4],
  x = 0.025, 
  y = seq(1, 0.25, by = -0.25) - 0.01
)
for(i in seq_len(nrow(label_tbl))) {
  p_out <- p_out + 
    cowplot::draw_text(
      text = label_tbl$lbl[i],
      x = label_tbl$x[i],
      y = label_tbl$y[i]
    )
}


plot_frac <- 0.95
plot_legend_add_height <- 0
p_test_full <- cowplot::ggdraw() + 
  cowplot::draw_plot(
    plot = p_out, 
    height = plot_frac, 
    y = 1 - plot_frac
  ) +
  cowplot::draw_plot(
    plot = p_legend, 
    y = 0, 
    x = 0, 
    width = 1, 
    height = 1 - plot_frac + plot_legend_add_height
  )

path_fig_rel_pdf <- file.path(
    dir_fig_vec_rel["manu"],
    "supp_fig_2.pdf"
  )
path_fig_rel_png <- file.path(
    dir_fig_vec_rel["manu"],
    "supp_fig_2.png"
  )

cowplot::ggsave2(
  path_fig_rel_png, 
  p_test_full, 
  height = 29.4, 
  width = 19, 
  units = "cm",
  dpi = 300 * (1 + params$high_res * 4)
)

cowplot::ggsave2(
  path_fig_rel_pdf, 
  p_test_full, 
  height = 29.4, 
  width = 19, 
  units = "cm",
  dpi = 300 * (1 + params$high_res * 4)
)
```

```{r , results = "asis"}
knitr::include_graphics(path_fig_rel_png)
```

```{r }
if (dir.exists("/home/rstudio/ProjectGelaDURT")) {
  dir_output <- file.path(
    "/home/rstudio/ProjectGelaDURT",
    "Output", "figures", "manuscript"
    )
  if (dir.exists(dir_output)) unlink(dir_output, recursive = TRUE)
  dir.create(dir_output, recursive = TRUE)
  fn_vec <- list.files("_book/figures/manuscript")
  for (x in fn_vec) {
    file.copy(
      file.path("_book/figures/manuscript", x),
      file.path(dir_output, x)
    )
  }
}
```
